Draft1

### 2014-12-12 PresentationandPaper/Draft1.Rmd
Edited stargazer table

(Take this for the paper)

@@

stargazer::stargazer(Z1, Z2, covariate.labels = labels, dep.var.labels = dlabels,
                     title = 'Linear Regression Estimates', notes = "Regression equation 1 is unimputed, regression equation 2 is imputed", digits = 2, type = 'latex')

@@

```{r echo = FALSE, cache=TRUE, include=TRUE, results='asis', warning=FALSE}

>>>>

@@

stargazer::stargazer(Z1, Z2,
                     title = 'Linear Regression Estimates', notes = "Regression equation 1 is unimputed, regression equation 2 is imputed", digits = 2, type = 'latex')

@@

```{r echo = FALSE, cache=TRUE, include=FALSE, results='asis', warning=FALSE}
